---
title: "Reproducible Research Project"
author: "Dimas Adinugroho"
date: "24 Mei 2016"
output: html_document
---

# Reproducible Research 

## Introduction

It is now possible to collect a large amount of data about personal movement
using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone
Up. These type of devices are part of the “quantified self” movement – a group
of enthusiasts who take measurements about themselves regularly to improve
their health, to find patterns in their behavior, or because they are tech geeks.
But these data remain under-utilized both because the raw data are hard to
obtain and there is a lack of statistical methods and software for processing and
interpreting the data.

This assignment makes use of data from a personal activity monitoring device.
This device collects data at 5 minute intervals through out the day. The data
consists of two months of data from an anonymous individual collected during
the months of October and November, 2012 and

## Data

The variables included in this dataset are:

* ``steps``: Number of steps taking in a 5-minute interval (missing values are
coded as NA)
* ``date``: The date on which the measurement was taken in YYYY-MM-DD
format
* ``interval``: Identifier for the 5-minute interval in which measurement was
taken

## Loading and preprocessing the data

```{r, cache=TRUE,results = "hide"}
library (plyr)
library (dplyr)
library (ggplot2)

files = 'activity.csv'
activity <- read.csv(files,header=TRUE,sep=",", colClasses = c('integer', 'Date', 'integer'))
```

## What is mean total number of steps taken per day?

```{r, cache=TRUE}
library (ggplot2)
totalstepperday <- ddply(activity, .(date), summarize, step = sum(steps), mean = mean(steps))
totalstepperday [is.na(totalstepperday )] <- 0
summary(totalstepperday$step)
```


```{r}
library (ggplot2)
plot1 <- ggplot(totalstepperday, aes(x = date, y = step, colour="black", fill="red")) + geom_bar(stat = "identity")
plot1
```


## What is the average daily activity pattern?
```{r}
library (plyr)
library (ggplot2)
daily_act <- activity
daily_act [is.na(daily_act)] <- 0
interv <- ddply(daily_act, .(interval), summarize, step = mean(steps))
plot2 <- ggplot(data = interv, aes(interval, step)) + geom_line(colour="red")
plot2
```

```{r}
interv[interv$step == max(interv$step),]
```

## Inputing missing values

```{r}
missing <- sum(is.na(activity$steps))
missing
```

```{r}
activity_NA <- transform(activity, steps = ifelse(is.na(steps), round(mean(steps, na.rm=TRUE)), steps))
summary(activity_NA)
```

```{r}
totalstepperday_NA <- ddply(activity_NA, .(date), summarize, step = sum(steps))
plot3 <- ggplot(totalstepperday_NA, aes(x = date, y = step, colour="black", fill="red")) + geom_bar(stat = "identity")
plot3
```

## Are there differences in activity patterns between weekdays and weekends?

```{r}
library (lubridate)
activity_NA_date <- transform(activity_NA, week = ifelse(wday(date, label= TRUE) == 'Sun' | wday(date, label= TRUE) == 'Sat' , "Weekends" , "Weekdays"))
endorweek <- ddply(activity_NA_date, .(week, interval), summarize, steps = mean(steps))
plot4 <- qplot(interval, steps, data = endorweek, color = week, facets = week ~ ., geom = c("line"))
plot4
```
